\chapter{Operations}

\section{Overview}

We now explicitly define our interpretation of the detected operations on fields
and methods in terms the field and method key/value definitions. Class 1 and
class 2 refer to the two Java input files.

\section{Output Format}

The output format for a particular operation is:\\

\begin{lstlisting}[frame=single]
$OP: $key$NL
\end{lstlisting}


Where ``\$OP'' is one of the operations listed below, ``\$key'' is either
a method key or a field key, and ``\$NL'' is the newline character (ASCII value
0xA). The full program output is a series of outputs for each particular
operation.

\section{Operation Outputs}

\subsection{No Change}

If a field or method remains unchanged, there is no output.

\subsection{AM: Add a new method}

We mark a method as \textbf{AM} when the method key is present in class 1,
but the method key is not present in class 2.

\subsection{DM: Delete a method}

We mark a method as \textbf{DM} when the method key is present in class 1, but
the method key is not present in class 2.

\subsection{CM: Change the body of a method}

We mark a method as \textbf{CM} if the method key is present in both class 1
and class 2, but the text body of a method has changed.
Note that this comparison is done with a simple string comparison.

\subsection{AF: Add a field}

We mark a field as \textbf{AF} if the field key is not present in class 1,
but the field key is present in class 2.

\subsection{DF: Delete a field}

We mark a field as \textbf{DF} if the field key is present in class 1, but the
field key is not present in class 2.

\subsection{CFI: Change field initializer}

We mark a field as \textbf{CFI} if the field key is present in both class 1
and class 2, but the field value has changed.

\section{Sample Output}

See Figure \ref{figure:sample-output} for a sample jsrcdiff output, and
see Appendix \ref{appendix:input-files} for the two input files used to
produce this output.

\begin{figure}
\centering
\begin{lstlisting}[frame=single]
CM: void method0()
CM: void method1()
DM: String method4(int, double)
DM: double method5(String)
DM: double method6(Map<String,String>)
DM: int method2(int)
DM: int method3(int)
AM: String method4(int, double, String)
AM: double method2(int)
AM: double method5(Map<String,String>)
AM: double method7(String)
AM: int method3(double)
CFI: int i
CFI: int[] intArr1
CFI: String stringDoubleArr
CFI: String s
CFI: int x
DF: HashMap<String,String> map0
DF: int intArr2
DF: int intDeepArr2
DF: int[][][][][][] intDeepArr1
AF: HashMap<String,String> mapXXX
AF: double intDeepArr2
AF: int intArr3
AF: int[][][][][][][] intDeepArr1
\end{lstlisting}
\caption{A sample jsrcdiff output}
\label{figure:sample-output}
\end{figure}
